A Survey of Near-Term Exoskeleton Technology\\ (Draft 3.0)

### 2015-09-30 technology.tex

Here are some actuation types that have not been adequately explored
in humanoid robots and exoskeletons.

@@

>>>>

Here are some actuators
that have not been adequately explored
in humanoid robots and exoskeletons.

@@

\section{Multi-joint actuators and mechanical linkages}

Actuators and mechanical linkages that cross more than one joint
can be used to improve energy efficiency by cancelling positive
work done at one joint with negative work at another joint.
Figure~\ref{f:hip-knee} shows how biarticular muscles can be used
in human running to transfer energy across joints.

\begin{figure}[t]
\centering
\includegraphics[width=0.75\textwidth]{figs/shc1}
\caption{From xxx}
\label{f:hip-knee}
\end{figure}
